Making multiple-locus association mapping on a genome-wide scale routine

### 2017-11-08 AM+draft.tex
08Nov17 Morning - methods

@@

gemma

>>>>

We compared the performance of Eagle against five other multiple locus association mapping methods: BigRR, 
glmnet, FaST-LASSO, MMLM, and r2VIM.  These five methods were selected because of their demonstrated value 
for analysing genetic data, they reflect a range of different statistical methodologies for association mapping, and they are available as 
either stand-alone computer programs or as  packages. A summary of how the computer programs/packages differ in their 
features is given in Table X.

BigRR, FaST-LASSO, and glmnet are all based on regularization methods. Regression based regularization methods 
are well suited to solving problems where the number of predictors (p) is far greater than the number of samples (n).  It 
should come as no surprise then that multiple locus association mapping are dominated by regularization-based approaches.
Regularisation methods are able to yield solutions to problems that OLS cannot. They introduce a penalty function that balances
bias against reduced variance.  BigRR, an R package, implements gen

BigRR is an R package that implements

$------$

@@

\textbf{FaST-LMM:}  FaST-LMM is a highly efficient stand along computer program for association 
mapping \cite{lippert2011fast}. It is based on a standard single-locus model 
\cite{yu2006unified,zhao2007arabidopsis}. Its computational efficiencies come through factorising $K$ with spectral decomposition so that $K=U (S + \delta I) U^T$ where $U$ contains the eigenvectors and $\delta$ is the ratio of the genetic variance to the residual variance. 
By rotating the data with $U$, the log likelihood of the linear mixed model can be expressed as the log likelihood for a simple 
linear model.  This greatly reduces the computational cost of performing lmm-based  association mapping. With FaST-LMM, 
analyses scale linearly with sample size $n$, both in terms of run-time and memory usage.

\textbf{gemma}
